A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-06-04 paper/main.tex
overall revision to improve flow of reading

\todo[inline]{revised: data-driven vs./in combination (with) model-driven}
% data-driven methods
Because naturalistic stimuli are multi-dimensional and their temporal structure
is usually unknown, data-driven methods like intersubject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data. However, data-driven methods alone fall usually short
of pinpointing their results to specific, time-locked features of a stimulus
\citep{kauttonen2015optimizing}.
% model-driven methods
Model-driven methods, like a general linear model (GLM), can be useful to
investigate how hemodynamic brain responses in isolated regions correlate with
stimulus features. They can explain not just ``how'' the brain is responding to
a stimulus but also ``why'' \citep{hamilton2018revolution}.
% GLM: example studies
For example, studies using GLMs based on annotations of a stimulus' temporal
structure have elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.
% combination of data-driven and model-driven approaches
Additionally, stimulus annotations can inform data-driven methods about a
stimulus' temporal dynamics, or model-driven and data-driven methods can be
combined to improve interpretability of results \citep{lahnakoski2012stimulus}.

\todo[inline]{revised: why this anno is better than any previous anno and worth
being published as a paper}
% we:
For this publication, we revised previous, preliminary annotations done by our
lab and now provide one single annotation with exact onsets/offsets and content
of each sentences, word and phonemes (see Table \ref{tab:overview} for an
overview) spoken in the audio-visual movie ``Forrest Gump''
\citep{ForrestGumpMovie} and its audio-description (i.e. an audio-only variant
of the movie)\citep{ForrestGumpDVD}.
% the studyforrest dataset
fMRI data of participants watching the audio-visual movie
\citep{hanke2016simultaneous} and listening to the audio-description
\citep{hanke2014audiomovie} are the core data of the publicly available
\textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
% why even bother?
This publication enables researchers to model hemodynamic brain responses that
correlate with a variety of time-locked aspects of spoken language ranging from
a speaker's identity, to phonology, grammar, and semantics.
% extending previous non-speech annotations
The current annotation of speech extends already available annotations of
portrayed emotions \citep{labs2015portrayed}, perceived emotions
\citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the
movie \citep{haeusler2016annotation}. All annotations can be used in any study
focusing on aspects of real-life cognition by serving as additional confound
measures describing key properties of major building blocks of the stimulus.

@@

\subsection*{Annotation procedure}
% preliminary annotations
Preliminary, manual orthographic transcriptions of dialogues, non-speech
vocalizations (e.g. laughter or groaning) and script for the audio-description's
narrator were merged, and converted to Praat's \citep{boersma2019praat} TextGrid
format.
% preparing annotation in Praat before forced alignment
% \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
The merged transcription containing a rough onset and offset for usually a
couple of sentences was edited in Praat for manual validation against the
original audio.
% steps conducted
The following steps were done in several passes to iteratively improve the
quality of the data: approximate temporal onsets and offsets were corrected, and
intervals containing several sentences were split into intervals containing only
one sentence.
% dropping of sentences hard to understand
When two or more persons were speaking simultaneously the less dominant voice
was dropped. Low volume background speech (especially occurring during music or
continuous environmental noise) or low volume non-speech vocalizations which
were subjectively assessed to be incomprehensible for the audience were dropped,
too.
% intro for forced aligner
We used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
algorithmically identify the exact onset of offset of the sentences, and the
onset and offset of each word and phoneme embedded in the transcribed sentences.
% preparing other inputs before forced alignment pronunciation dictionary
% http://prosodylab.org
% https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
To enable the aligner to look up the phonemes embedded within each word, we
chose a German pronunciation dictionary provided by Prosodylab \citep
{gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the
pronunciation of phonemes.
% extending the dictionary with formerly unknown German words
To improve the detection rate of the automatic alignment, the dictionary was
manually updated with German words that occur in the stimuli but were originally
missing in the dictionary.
% \href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict}
% English words in the otherwise German stimulus
The pronunciation of English words and phonemes occurring in the otherwise
German audio track was taken from an English pronunciation dictionary (following
the ARPAbet PhoneSet) provided by the Montreal Language Modeling lab
(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).

@@

% natural language processing (NLP)
% spaCy
To automatically analyze linguistic features of each words in their
corresponding sentence, we employed the Python package spaCy \citep{spacy2} and
its accompanying German language model (\texttt{de\_core\_news\_md} that was
trained on the TIGER Treebank corpus \citep{brants2004tiger}.
% Tiger Treebank Corpus:
% \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.
% dropping of non-speech vocalizations because they often delude the algo
Non-speech vocalizations were dropped from the sentences before analysis to
improve results.
% performed analyses
We performed analyses regarding part-of-speech (i.e. grammatical tagging or
word-category disambiguation), syntactic dependencies, lemmatization, word
embedding (i.e. multi-dimensional meaning representation of a word), and if the
word is one of the most common words of the German language (i.e. if the word is
part of a stop list).

@@

\subsubsection*{Simple part-of-speech tag (\texttt{pos})} A simple
part-of-speech tagging (grammatical tagging; word-category disambiguation) of a
word.
% annotation scheme
The simple part-of-speech tagging tags follow the Universal Dependencies v2 POS
tag set (\href{https://universaldependencies.org}{universaldependencies.org}).
% reference to table
See Table \ref{tab:pos} for a description of the labels and the respective
counts of all 15 labels. Nouns that spaCy mistook for proper nouns or vice
versa were corrected via script.
% s. list at the beginning of script code/add_part-of-speech-tagging2textgrid.py
% flags for sentences and phonemes in POS column
Additionally in cells of this column, sentences are tagged as \texttt{SENTENCE},
and phonemes are tagged as \texttt{PHONEME} to facilitate sorting, and filtering
in potential further processing steps.

@@

\subsubsection*{Detailed part-of-speech tag (\texttt{tag})}
% \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset}
A detailed part-of-speech tagging of a word following the TIGER Treebank
annotation scheme \citep{brants2004tiger} which is based on the
Stuttgart-Tübingen-Tagset \citep{schiller1999stts}.
% reference to table
See Table \ref{tab:tag} for a descripion  of the labels and the respective
counts of the 15 most often occuring labels. Nouns that spaCy mistook for proper
nouns or vice versa were corrected via script.
% s. list at the beginning of script code/add_part-of-speech-tagging2textgrid.py

@@

\subsubsection*{Syntactic dependency (\texttt{dep})} Information about a word's
syntactic dependencies with other words within the same sentence.
% annotation scheme
Information follows the TIGER Treebank annotation scheme \citep{brants2004tiger}
and is given in the format: ``arc label;word's head;word's child1, word's
child2, ...'', where the ``arc label'' (see Table \ref{tab:dep}) describes the
type of syntactic relation that connects a "child" (the single word) to its
"head".

@@

\subsubsection*{Word embedding (\texttt{vector})}
% \href{https://en.wikipedia.org/wiki/Word2vec}{word vector}
A 300-dimensional word vector providing a multi-dimensional meaning representation of a word.
Out-of-vocabulary words with a vector consisting of 300 dimensions of zeroes were set to \texttt{\#} to save space.

\subsection*{Dataset content}
% \href{https://bids.neuroimaging.io/}{bids.neuroimaging.io}
The released annotation comes in two different versions. First, as a text-based TextGrid file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}) to be conveniently edited with the software Praat \citep{boersma2019praat}.
Second, as a text-based, tab-separated-value (TSV) formatted table  (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS} \citep{gorgolewski2016bids}).
The source code for all descriptive statistics included in this paper is available in \texttt{code/descriptive-statistics.py} (Python script).

\section*{Dataset validation}
% Information about any validation carried out and/or any limitations of the
% datasets, including any allowances made for controlling bias or unwanted
% sources of variability. ~170 words => das wird beim folgenden Schreiben
% definitiv nichts werden intro
In order to assess data quality, we investigated if contrasting speech-related
events to events without speech lead to increased activation in areas known to
be involved in semantic processing \citep{hickok2007cortical}.
% nouns and proper nouns resp. > coordinate junctions
Moreover, we tested if similar linguistic concepts providing high semantic
information (proper nouns and nouns) contrasted to a concept providing low
semantic information (coordinate conjunctions) lead to increased activation in
congruent brain areas.
% data source
% data aligned by applying an affine transformation only are available in
% bold_dico_dico7Tad2grpbold7Tad.nii.gz.
% data aligned by non-linear warping are available in
% bold_dico_dico7Tad2grpbold7Tad_nl.nii.gz.
We used a dataset providing blood oxygenation level-dependent (BOLD) functional
magnetic resonance imaging (fMRI) data of 20 subjects (age 21–38 years, mean age
26.6 years, 12 male) listening to the 2h audio-description (\unit[7]{Tesla},
\unit[2]{s} repetition time, 3599 volumes, 36 axial slices, thickness
\unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm}
field-of-view) \citep{hanke2014audiomovie}.
% motion correction
Data were already corrected for motion at the scanner computer.
% alignment
Further, individual BOLD time-series were already aligned by non-linear warping
to a study-specific T2*-weighted echo planar imaging (EPI) group template (cf.
\citep{hanke2014audiomovie} for details on how the group template was created).
% steps done by C.H.
All further analysis steps were carried out using Feat v6.00 (FMRI Expert
Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB's
Software Library)\citep{smith2004fsl}.
% dropping of subject 10
Data of one participant were dropped to due to invalid distortion correction
during scanning.
% temporal and spatial filter, brain extraction
Data were temporally high-pass filtered (cut-off \unit[150]{s}), spatially
smoothed (Gaussian kernel; \unit[4.0]{mm} FWHM), and the brain was extracted
from surrounding tissue.
% normalization
A grand-mean intensity normalization of the entire 4D dataset was performed by a
single multiplicative factor.

@@

    \caption{Overview of the events that were used to create the 26 regressors of the GLM analysis.

@@

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors based on events drawn from the annotation (see Table
\ref{tab:regressors}).
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word \todo{This has errors that I do not know how
to fix; sorry, unclear what you mean by that}.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
function from onset to offset of the corresponding word\todo{I do not know what
this mean; CH: hope it got clearer now}.
% phonemes
The top 80 phonemes (\texttt{n} with N=6053 to \texttt{IY1} with N=32) were
pooled to \texttt{phonemes} (N=\rPhonesAll) and each event modeled as boxcar
function from onset to offset of the corresponding phoneme.\todo{Does that mean
    they share events with "other"; CH: dunno what you mean, but text should be
clearer now}.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance correlating with sentence comprehension.
\todo{Why? Above it says 'we tested if similar linguistic concepts providing
    high semantic information (proper nouns and nouns)'. What does this need
sentences for? CH: it is kinda nuisance regressor}
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
longer lasting intervals between onsets and offsets of words and thus within
intervals without audible speech \todo{Why assumed? Isn't the point of the
annotation to "know"? CH: words where chosen to carefully; intervals don't
contain any audible speech with >98 perc. certainty}
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the average
length of phonemes.
% low-level nuisance regressors
Lastly, we used events\todo{They are not really events, but a continuous
nuisance regressor; CH: okay, how do you phrase that correctly?} reflecting
low-level auditory features (left-right difference in volume and root mean
squared volume) averaged across the length of every movie frame (\unit[40]{ms}).
All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the
hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix and the design was
subjected to the same temporal filtering as the BOLD time series.
% motion parameters
Finally, six motion parameters were used as additional nuisance regressors.

@@

% 2nd lvl
The second-level analysis which averaged contrast estimates across the eight
stimulus segments per subject was carried out using a fixed effects model by
forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of
Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
% 3rd lvl
The third level analysis which averaged contrast estimates across subjects was
carried out using FLAME stage 1 with automatic outlier de-weighting
\citep{woolrich2004multilevel, woolrich2008robust}.
% thresholding
Z (Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a corrected cluster significance threshold of p<.05
\citep{woolrich2008robust}.
% identification of brain regions
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.

% Results
Figure \ref{fig:results} depicts the results of the three contrasts (Z threshold
Z>3.4; p<.05 cluster-corrected).
% COPE 1:
The contrast words (all 21 \texttt{tag-related} regressors) > no-speech yielded
four significant clusters (see Table \ref{tab:cope1}):
% cluster 1
one left lateralized cluster spanning from the angular gyrus and inferior
posterior supramarginal gyrus across the superior and middle temporal gyrus,
including parts of Heschl's gyrus and planum temporale.
% cluster 2
A second left cluster in (inferior) frontal regions, including precentral gyrus,
pars opercularis (Brodmann Areal 44; BA44) and pars triangularis (BA45).
% cluster 3
Similarly in the right hemisphere, one cluster spanning from the angular gyrus
across the superior and middle temporal gyrus but including frontal inferior
regions (pars opercularis and pars triangularis).
% cluster 4
A fourth significant cluster is located in the left thalamus.

% COPE 3
The contrast proper nouns > coordinate conjunctions yielded 9 significant
clusters (see Table \ref{tab:cope3}):
% cluster 1
one left lateralized cluster spanning from the angular gyrus across planum
temporale and superior temporal gyrus, partially covering the Heschl's gyrus,
into the anterior middle temporal gyrus.
% cluster 2
A largely congruent but smaller cluster in the right hemisphere.
% cluster 3 & 5, and 4 & 6
Two clusters in posterior cingulate cortex and precuneus of both hemispheres.
% remaining 3 clusters of COPE 3
Three small clusters in the right occipital pole, right Heschl's gyrus and left
superior lateral occipital pole.

% COPE 5
The contrast nouns > coordinate conjunctions yielded 4 significant clusters (see Table \ref{tab:cope5}):
% cluster 1 & 2
two clusters that are slightly smaller than lateral temporal clusters of contrast nouns > coordinate conjunction. In this case, spanning from angular gyrus in the left hemisphere and from planum temporale in the right hemisphere into the anterior part of superior temporal cortex.
% cluster 3 & 4
Finally, two small right lateralized clusters in the right posterior cingulate
gyrus and right precuneus.

>>>>

\todo[inline]{revised: data-driven vs./in combination (with) model-driven}
% data-driven methods
Because naturalistic stimuli are multi-dimensional and their temporal structure
is usually unknown, data-driven methods like intersubject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data. However, data-driven methods alone fall usually short
of pinpointing their results to specific, time-locked stimulus features \citep{kauttonen2015optimizing}.
% model-driven methods
Model-driven methods, like a general linear model (GLM), can be useful to
investigate how hemodynamic brain responses in isolated regions correlate with
stimulus features. They can explain not just ``how'' the brain is responding to
a stimulus but also ``why'' \citep{hamilton2018revolution}.
% GLM: example studies
For example, studies using GLMs based on annotations of a stimulus' temporal
structure have elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.
% combination of data-driven and model-driven approaches
Additionally, stimulus annotations can inform data-driven methods about a
stimulus' temporal dynamics, or model-driven and data-driven methods can be
combined to improve interpretability of results \citep{lahnakoski2012stimulus}.

\todo[inline]{revised: why this anno is better than any previous anno and worth
being published as a paper}
% we:
For this publication, we revised previous, preliminary annotations done by our
lab and now provide one single annotation with exact onset and offset of each
sentence, word and phoneme (see Table \ref{tab:overview} for an overview) spoken
in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
audio-description (i.e. the audio-only variant of the
movie)\citep{ForrestGumpGermanAD}.
% the studyforrest dataset
fMRI data of participants watching the audio-visual movie
\citep{hanke2016simultaneous} and listening to the audio-description
\citep{hanke2014audiomovie} are the core data of the publicly available
\textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
% why even bother?
This publication enables researchers to model hemodynamic brain responses that
correlate with a variety of aspects of spoken language ranging from a speaker's
identity, to phonology, grammar, and semantics.
% extending previous non-speech annotations
The current annotation of speech extends already available annotations of
portrayed emotions \citep{labs2015portrayed}, perceived emotions
\citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the
movie \citep{haeusler2016annotation}. All annotations can be used in any study
focusing on aspects of real-life cognition by serving as additional confound
measures describing key properties of major building blocks of the stimulus.

@@

\subsection*{Annotation procedure}
% preliminary annotations
Preliminary, manual orthographic transcriptions of dialogs, non-speech
vocalizations (e.g. laughter or groaning) and script for the audio-description's
narrator were merged and converted to Praat's \citep{boersma2019praat} TextGrid
format.
% preparing annotation in Praat before forced alignment
% \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
The merged transcription containing a rough onset and offset for usually a
couple of sentences was edited in Praat for manual validation against the
original audio.
% steps conducted
The following steps were done in several passes to iteratively improve the
quality of the data: approximate temporal onsets and offsets were corrected, and
intervals containing several sentences were split into intervals containing only
one sentence.
% dropping of sentences hard to understand
When two or more persons were speaking simultaneously the less dominant voice
was dropped. Low volume background speech (especially occurring during music or
continuous environmental noise) or low volume non-speech vocalizations which
were subjectively assessed to be incomprehensible for the audience were dropped,
too.
% intro for forced aligner
We then used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
algorithmically identify the exact onset of offset of each sentence, and the
onset and offset of each word and phoneme.
% preparing other inputs before forced alignment pronunciation dictionary
% http://prosodylab.org
% https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
To enable the aligner to look up the phonemes embedded within each word, we
chose a German pronunciation dictionary provided by Prosodylab \citep
{gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the
pronunciation of phonemes.
% extending the dictionary with formerly unknown German words
To improve the detection rate of the automatic alignment, the dictionary was
manually updated with German words that occur in the stimuli but were originally
missing in the dictionary.
% \href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict}
% English words in the otherwise German stimulus
The pronunciation of English words and phonemes occurring in the otherwise
German audio track was taken from an English pronunciation dictionary (following
the ARPAbet PhoneSet) provided by the Montreal Language Modeling lab
(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).

@@

% natural language processing (NLP) spaCy
To automatically analyze linguistic features of each word in their corresponding
sentence, we employed the Python package spaCy \citep{spacy2} and its
accompanying German language model (\texttt{de\_core\_news\_md} that was trained
on the TIGER Treebank corpus \citep{brants2004tiger}.
% Tiger Treebank Corpus:
% \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.  dropping of
% non-speech vocalizations because they often delude the algo
Non-speech vocalizations were dropped from the sentences before analysis to
improve results.
% performed analyses
We then performed analyses regarding part-of-speech (i.e. grammatical tagging or
word-category disambiguation), syntactic dependencies, lemmatization, word
embedding (i.e. a multi-dimensional meaning representation of a word), and if
the word is one of the most common words of the German language (i.e. if the
word is part of a stop list).

@@

\subsubsection*{Simple part-of-speech tag (\texttt{pos})} A simple
part-of-speech tagging (grammatical tagging; word-category disambiguation) of
words.
% annotation scheme
The tag labels of this simple part-of-speech tagging follow the Universal
Dependencies v2 POS tag set
(\href{https://universaldependencies.org}{universaldependencies.org}).
% reference to table
See Table \ref{tab:pos} for a description of the labels and the respective
counts of all 15 labels. Nouns that spaCy mistook for proper nouns or vice versa
were corrected via script.
% s. list at the beginning of script code/add_part-of-speech-tagging2textgrid.py
% flags for sentences and phonemes in POS column
Additionally in cells of this column, sentences are tagged as \texttt{SENTENCE},
and phonemes are tagged as \texttt{PHONEME} to facilitate sorting, and filtering
in potential further processing steps.

@@

\subsubsection*{Detailed part-of-speech tag (\texttt{tag})}
% \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset}
A detailed part-of-speech tagging of words following the TIGER Treebank
annotation scheme \citep{brants2004tiger} which is based on the
Stuttgart-Tübingen-Tagset \citep{schiller1999stts}.
% reference to table
See Table \ref{tab:tag} for a descripion  of the labels and the respective
counts of the 15 most often occuring labels (overall 43 labels). Nouns that
spaCy mistook for proper nouns or vice versa were corrected via script.
% s. list at the beginning of script code/add_part-of-speech-tagging2textgrid.py

@@

\subsubsection*{Syntactic dependency (\texttt{dep})} Information about a word's
syntactic dependencies with other words within the same sentence.
% annotation scheme
Information follows the TIGER Treebank annotation scheme \citep{brants2004tiger}
and is given in the format: ``arc label;word's head;word's child1, word's
child2, ...'', where the ``arc label'' (see Table \ref{tab:dep}) describes the
type of syntactic relation that connects a "child" (the single word) to its
``head''.

@@

\subsubsection*{Word embedding (\texttt{vector})}
% \href{https://en.wikipedia.org/wiki/Word2vec}{word vector}
A 300-dimensional word vector providing a multi-dimensional meaning
representation of a word.
% handling of words unknown to the model
Out-of-vocabulary words with a vector consisting of 300 dimensions of zeroes
were set to \texttt{\#} to save space.

\subsection*{Dataset content}
% \href{https://bids.neuroimaging.io/}{bids.neuroimaging.io} TextGrid format
The annotation comes in two different versions. First, as a text-based TextGrid
file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}) to be
conveniently edited with the software Praat \citep{boersma2019praat}.
% TSV format
Second, as a text-based, tab-separated-value (TSV) formatted table
(\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with
the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}
\citep{gorgolewski2016bids}).
% source code for descriptive statistics
The source code for all descriptive statistics included in this paper is
available in \texttt{code/descriptive-statistics.py} (Python script).

\section*{Dataset validation}
% Information about any validation carried out and/or any limitations of the
% datasets, including any allowances made for controlling bias or unwanted
% sources of variability. ~170 words => das wird beim folgenden Schreiben
% definitiv nichts werden
% intro
In order to assess data quality, we investigated if contrasting speech-related
events to events without speech lead to increased activation in areas known to
be involved in semantic processing \citep{hickok2007cortical}.
% nouns and proper nouns resp. > coordinate junctions
Moreover, we tested if similar linguistic concepts providing high semantic
information (proper nouns and nouns) contrasted to a concept providing low
semantic information (coordinate conjunctions) lead to increased activation in
congruent brain areas.
% data source
% data aligned by applying an affine transformation only are available in
% bold_dico_dico7Tad2grpbold7Tad.nii.gz.
% data aligned by non-linear warping are available in
% bold_dico_dico7Tad2grpbold7Tad_nl.nii.gz.
We used a dataset providing blood oxygenation level-dependent (BOLD) functional
magnetic resonance imaging (fMRI) data of 20 subjects (age 21–38 years, mean age
26.6 years, 12 male) listening to the 2h audio-description (\unit[7]{Tesla},
\unit[2]{s} repetition time, 3599 volumes, 36 axial slices, thickness
\unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm}
field-of-view) \citep{hanke2014audiomovie}.
% motion correction
Data were already corrected for motion at the scanner computer.
% alignment
Further, individual BOLD time-series were already aligned by non-linear warping
to a study-specific T2*-weighted echo planar imaging (EPI) group template (cf.
\citep{hanke2014audiomovie} for details on how the group template was created).
% steps done by C.H.
All further analysis steps were carried out using Feat v6.00 (FMRI Expert
Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB's
Software Library)\citep{smith2004fsl}.
% dropping of subject 10
Data of one participant were dropped to due to invalid distortion correction
during scanning.
% temporal and spatial filter, brain extraction
Data were temporally high-pass filtered (cut-off \unit[150]{s}), spatially
smoothed (Gaussian kernel; \unit[4.0]{mm} FWHM), and the brain was extracted
from surrounding tissue.
% normalization
A grand-mean intensity normalization of the entire 4D dataset was performed by a
single multiplicative factor.

@@

    \caption{Overview of events that were used to create the 26 regressors of the GLM analysis.

@@

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors based on events drawn from the annotation (see Table
\ref{tab:regressors}).
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word \todo{This has errors that I do not know how
to fix; COH: sorry, unclear what you mean by that}.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
function from onset to offset of the corresponding word\todo{I do not know what
this mean; CH: hope it got clearer now}.
% phonemes
The 80 most often occurring phonemes (\texttt{n} with N=6053 to \texttt{IY1}
with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and each event
modeled as boxcar function from onset to offset of the corresponding
phoneme.\todo{Does that mean they share events with "other"; CH: dunno what you
mean, but text should be clearer now}.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance correlating with sentence comprehension.
\todo{Why? Above it says 'we tested if similar linguistic concepts providing
    high semantic information (proper nouns and nouns)'. What does this need
sentences for? CH: it is kinda nuisance regressor}
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
longer lasting intervals between onsets and offsets of words and thus within
intervals without audible speech \todo{Why assumed? Isn't the point of the
annotation to "know"? CH: words where chosen to carefully; intervals don't
contain any audible speech with >98 perc. certainty}
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the
average length of phonemes.
% low-level nuisance regressors
Lastly, we used continuous information about auditory features (left-right
difference in volume and root mean squared volume) that was averaged across the
length of every movie frame (\unit[40]{ms}) to capture variance correlating with
low-level perceptual processes.
% convolving
Time series of events were convolved with FSL's ``Double-Gamma HRF'' as a model
of the hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix to compensate for
regional differences between modeled and actual HRF.
% motion parameters & temporal filtering of design
% motion parameter are filtered, too. See FSL manual:
% ``All (confound) EVs will be filtered to match the processing applied to the
% input data''
Finally, six motion parameters were used as additional nuisance regressors and
the design was subjected to the same temporal filtering as the BOLD time
series.

@@

% 2nd lvl
The second-level analysis which averaged contrast estimates across the eight
stimulus segments per subject was carried out using a fixed effects model by
forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of
Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
% 3rd lvl
The third level analysis which averaged contrast estimates across subjects was
carried out using FLAME stage 1 with automatic outlier deweighting
\citep{woolrich2004multilevel, woolrich2008robust}.
% thresholding
Z (Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a corrected cluster significance threshold of p<.05
\citep{woolrich2008robust}.
% identification of brain regions
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.

% Results
Figure \ref{fig:results} depicts the results of the three contrasts (Z threshold
Z>3.4; p<.05 cluster-corrected).
% COPE 1:
The contrast words > no-speech yielded four significant clusters (see Table
\ref{tab:cope1}):
% cluster 1
one left lateralized cluster spanning from the angular gyrus and inferior
posterior supramarginal gyrus across the superior and middle temporal gyrus,
including parts of Heschl's gyrus and planum temporale.
% cluster 2
A second left cluster in (inferior) frontal regions, including precentral gyrus,
pars opercularis (Brodmann Areal 44; BA44) and pars triangularis (BA45).
% cluster 3
Similarly in the right hemisphere, one cluster spanning from the angular gyrus
across the superior and middle temporal gyrus but including frontal inferior
regions (pars opercularis and pars triangularis).
% cluster 4
A fourth significant cluster is located in the left thalamus.

% COPE 3
The contrast proper nouns > coordinate conjunctions yielded nine significant
clusters (see Table \ref{tab:cope3}):
% cluster 1
one left lateralized cluster spanning from the angular gyrus across planum
temporale and superior temporal gyrus, partially covering the Heschl's gyrus,
into the anterior middle temporal gyrus.
% cluster 2
A largely congruent but smaller cluster in the right hemisphere.
% cluster 3 & 5, and 4 & 6
Two clusters in posterior cingulate cortex and precuneus of both hemispheres.
% remaining 3 clusters of COPE 3
Three small clusters in the right occipital pole, right Heschl's gyrus and left
superior lateral occipital pole.

% COPE 5
The contrast nouns > coordinate conjunctions yielded four significant clusters (see Table \ref{tab:cope5}):
% cluster 1 & 2
two clusters that are slightly smaller than lateral temporal clusters of contrast nouns > coordinate conjunction.
% variation in cluster 1 & 2 in comparison to COPE 1
In this case, spanning from angular gyrus in the left hemisphere and from planum temporale in the right hemisphere into the anterior part of superior temporal cortex.
% cluster 3 & 4
Finally, two small right lateralized clusters in the right posterior cingulate
gyrus and right precuneus.
